---
title: "Data-Cleaning_Close-to-Us-Away-From-Me "
author: "Lucas Gautier, Victor Auger, Rhéa Haddad"
date: '2022-11-24'
output: html_document
---
This script is the data cleaning of the project "Close-to-Us-Away-From-Me".
The Aim of this project is to study the influence of social class and self-models (independence/interdependence) on proxemic preferences



```{r}

# Set Up environments

cat("\014") # clear console
rm(list=ls()) # clear workspace

# Load packages

# 4 lines : Installs (if necessary) and loads the packages you enter in the 1st row
# 1st row : Creates a list of packages names that you want to use in the script (there is virtually no limit in how much package you can put here)
# 2nd row : Creates a list of packages that have not been installed yet (new packages)
# 3rd row : Installs the new packages
# 4th row : Loads all the listed packages
list.of.packages <- c("dplyr", "emmeans", "tidyverse", "readr", "psych", "lmerTest")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)
invisible(lapply(list.of.packages, require, character.only = TRUE))

rm(list=ls()) # clear workspace

set.seed(42) # set overall random seed for reproducibility
```

# Build the dataframe

## Questionnaire dataframe

Independance/interdependance scale

- Dependence1: I prefer to be self-reliant rather than depend on others.(Reverse item)
- Dependence2: I try not to depend on others. (Reverse item)
- Dependence3: I prefer to turn to other people for help rather than solely rely on myself 
- Dependence4 :It is important for me to act as an independent person. 
- Dependence5: I’m uncomfortable if I have to rely on myself. (Reverse item)
- Dependence6: I am similar to the people close to me.
- Dependence7: I feel my fate is intertwined with the fate of those around me. 
- Dependence8: It is important to consult close friends and get their ideas before making a decision. 
- Dependence9: I like sharing little things with my neighbours.


Self-reliance versus Dependence on others

- Connection1: I consider my happiness separate from the happiness of my friends and family. (Reverse item)
- Connection2: It is important for me to be an accepted member of my family as well as my group of friends.
- Connection3: I usually feel a strong sense of pride when someone in my family has an important accomplishment.
- Connection4: When I think of myself, I often think of my close friends and family also.
- Connection5: If a person hurts someone close to me, I feel personally hurt as well.
- Connection6: My close relationships are unimportant to how I feel about myself. (Reverse item)
- Connection7: My personal accomplishments are more important than maintaining my social relationships. (Reverse item)
- Connection8: I see my close relationships as separate from who I am as an individual. (Reverse item)
- Connection9: I usually feel a strong sense of pride when someone close to me has an important accomplishment.
- Connection10: If a person insults a member of my family or my friends, I feel personally insulted myself.
- Connection11: I always support a group decision even when I know it is wrong. (Reverse item)
- Connection12: My role within my family gives me a sense of who I am. 
- Connection13: I prefer to do what I want without letting my family or friends influence me. (Reverse item)
- Connection14: My happiness depends very much on the happiness of those around me. 


Difference versus Similarity

- Similarity1: I am a unique individual. (Reverse item)
- Similarity2: Being a unique individual is important to me. (Reverse item)
- Similarity3: I am a unique person, separate from others. (Reverse item)
- Similarity4: I enjoy being unique and different from others in many ways. (Reverse item)
- Similarity5: Being different from others makes me uncomfortable
- Similarity6: I avoid standing out among my friends.
- Similarity7: I feel good when I cooperate with others. 

PESS: 

- PESS1: My income is low compared to others
- PESS2: I feel that I have less money than I need
- PESS3: I find it difficult to pay my bills and basic needs
- PESS4: My income is insufficient to live decently 
- PESS5: I do not have enough money to cover all my monthly expenses
- PESS6: My limited income and savings make me uncertain about my future
- PESS7: I can't stop thinking about the lack of money
- PESS8: I worry about not having enough money


```{r}
tmp <- df <- read_csv("Data/data.csv")


names(tmp)[1] <- "Participant"
names(tmp)[2] <- "Exp_Name"
names(tmp)[3] <- "Money_Pb1"
names(tmp)[4] <- "Money_Pb2"
names(tmp)[5] <- "Money_Pb3"
names(tmp)[6] <- "Money_Pb4"
names(tmp)[7] <- "Money_Pb5"
names(tmp)[8] <- "Money_Pb6"
names(tmp)[9] <- "Money_Pb7"
names(tmp)[10] <- "Money_Pb8"
names(tmp)[11] <- "Money_Pb9"
names(tmp)[12] <- "Money_Pb10"
names(tmp)[13] <- "SES_Subjective"


# Independance/Interdependance scale

## Self-reliance versus Dependence on others
names(tmp)[14] <- "Dependence1" #(inverse item)
names(tmp)[15] <- "Dependence2" #(inverse item)
names(tmp)[16] <- "Dependence3" #(inverse item)
names(tmp)[17] <- "Dependence4" 
names(tmp)[18] <- "Dependence5" #(inverse item)
names(tmp)[19] <- "Dependence6" 
names(tmp)[20] <- "Dependence7" 
names(tmp)[21] <- "Dependence8" 
names(tmp)[22] <- "Dependence9" 

# Self-containment versus Connection to others
names(tmp)[23] <- "Connection1" #(inverse item)
names(tmp)[24] <- "Connection2" 
names(tmp)[25] <- "Connection3"
names(tmp)[26] <- "Connection4" 
names(tmp)[27] <- "Connection5"
names(tmp)[28] <- "Connection6" #(inverse item)
names(tmp)[29] <- "Connection7" #(inverse item)
names(tmp)[30] <- "Connection8" #(inverse item)
names(tmp)[31] <- "Connection9" 
names(tmp)[32] <- "Connection10"
names(tmp)[33] <- "Connection11" #(inverse item)
names(tmp)[34] <- "Connection12" 
names(tmp)[35] <- "Connection13" #(inverse item)
names(tmp)[36] <- "Connection14"

# Difference versus Similarity
names(tmp)[37] <- "Similarity1" #(inverse item)
names(tmp)[38] <- "Similarity2" #(inverse item)
names(tmp)[39] <- "Similarity3" #(inverse item)
names(tmp)[40] <- "Similarity4" #(inverse item)
names(tmp)[41] <- "Similarity5" 
names(tmp)[42] <- "Similarity6" 
names(tmp)[43] <- "Similarity7" 

warning("we need to check the constructvalidity of each scale before to build a mean composite score for each dimension of the interdependance/independance scale")

# PESS
names(tmp)[44] <- "PESS1"
names(tmp)[45] <- "PESS2" 
names(tmp)[46] <- "PESS3" 
names(tmp)[47] <- "PESS4" 
names(tmp)[48] <- "PESS5" 
names(tmp)[49] <- "PESS6" 
names(tmp)[50] <- "PESS7" 
names(tmp)[51] <- "PESS8" 

names(tmp)[52] <- "Logement_Type"
names(tmp)[53] <- "Logement_Type_Other" 
names(tmp)[54] <- "Logement_Size" 
names(tmp)[55] <- "Room_Nb" 
names(tmp)[56] <- "Household_Nb" 
names(tmp)[57] <- "Minors_Nb" 
names(tmp)[58] <- "Share_Commons" 
names(tmp)[59] <- "Town" 
names(tmp)[60] <- "Country" 
names(tmp)[61] <- "Study_Level" 
names(tmp)[62] <- "CSP" 
names(tmp)[63] <- "CSP_Other" 
names(tmp)[64] <- "Age" 
names(tmp)[65] <- "Gender" 
names(tmp)[66] <- "Time_Start" 
names(tmp)[67] <- "Time_End" 
names(tmp)[68] <- "Time_Total" 

df <- tmp

rm(list=setdiff(ls(), c("df"))) # clear workspace except the data frame

```

Create composite scores

```{r}
tmp <- df

tmp <-  tmp %>% 
  rowwise() %>%
  mutate(PESS_Mean = mean(c(PESS1, PESS2, PESS3, PESS4, PESS5, PESS6, PESS7, PESS8)))

# tmp <-  tmp %>% 
#   mutate(PESS_Mean = mean(c(PESS1, PESS2, PESS3, PESS4, PESS5, PESS6, PESS7, PESS8)))

tmp <- tmp %>% 
  rowwise() %>%
  mutate(Dependance_Mean = mean(c((8-Dependence1), (8-Dependence2), (8-Dependence3), Dependence4, (8-Dependence5), Dependence6, Dependence7, Dependence8, Dependence9)))

tmp <- tmp %>% 
  rowwise() %>%
  mutate(Connection_Mean = mean(c((8-Connection1), Connection2, Connection3, Connection4, Connection5, (8-Connection6), (8-Connection7), (8-Connection8), Connection9, Connection10, (8-Connection11), Connection12, (8-Connection13), Connection14)))

tmp <- tmp %>% 
  rowwise() %>%
  mutate(Similarity_Mean = mean(c((8-Similarity1), (8-Similarity2), (8-Similarity3), (8-Similarity4), Similarity5, Similarity6, Similarity7)))

df <- tmp

rm(list=setdiff(ls(), c("df"))) # clear workspace except the data frame

```


```{r}
describe(df$PESS_Mean)

explore(df)

```

Ctrl + Alt + I : nouveau chunk
